---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  cache = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "75%",
  dpi = 300,
  message = FALSE,
  warning = FALSE
  )
```

# Models of Motor Inhibition during Motor Imagery

[![GitHub repo size](https://img.shields.io/github/repo-size/lnalborczyk/momimi?color=brightgreen&logo=github)](https://github.com/lnalborczyk/momimi)
[![GitHub last update](https://img.shields.io/github/last-commit/lnalborczyk/momimi?color=brightgreen&logo=github)](https://github.com/lnalborczyk/momimi)

The `momimi` package implements different versions of the "threshold modulation model" (TMM3/TMM4) of motor imagery and provides fitting and plotting utilities.
    
## Installation

You can install the latest stable version of the package from GitHub with:

```{r installing, eval = FALSE}
# install.packages("devtools")
devtools::install_github(repo = "lnalborczyk/momimi", build_vignettes = TRUE)
```

## Usage

### Simulating and plotting data

We start by simulating some data (here, 100 observations or RTs and MTs).

```{r simulating1}
library(tidyverse)
library(momimi)

simulated_data <- model(
    nsims = 100, nsamples = 2000,
    exec_threshold = 1.1, imag_threshold = 0.55,
    peak_time = log(0.5), curvature = 0.5,
    model_version = "TMM3",
    full_output = TRUE
    )
```

We can plot the underlying activation function and the implied distributions of RTs and MTs.

```{r plotting}
# plotting only the latent function(s)
plot(x = simulated_data, method = "functions")

# plotting only the distributions of RTs/MTs distributions
plot(x = simulated_data, method = "distributions")
```

### Fitting the models

We can also use the model to generate realistic data from known parameter values and then fit the model (below, the 3-parameter version of the TMM) to these data to try recovering the original parameter values.

```{r simulating2}
# plausible "true" parameter values in the TMM3
# parameters are the motor execution threshold, the peak time, and the curvature
true_pars <- c(1.1, 0.5, 0.4)

# simulating data using these parameter values
simulated_data <- simulating(
    nsims = 200,
    nsamples = 3000,
    true_pars = true_pars,
    action_mode = "imagined",
    model_version = "TMM3"
    )

# displaying the first ten rows of these data
head(x = simulated_data, n = 10)
```

We fit the model and use realistic constraints (e.g., the RT/MT should be no less than 0.1s and no more than 2 seconds) on the initial parameter values (by setting `initial_pop_constraints = TRUE`) to facilitate convergence (fitting can take a while).

```{r fitting, results = "hide"}
# fitting the model
results <- fitting(
    data = simulated_data,
    nsims = 200,
    error_function = "g2",
    method = "DEoptim",
    model_version = "TMM3",
    lower_bounds = c(1.0, 0.3, 0.2),
    upper_bounds = c(1.4, 0.7, 0.6),
    initial_pop_constraints = TRUE,
    nstudies = 200,
    rt_contraints = range(simulated_data$reaction_time),
    mt_contraints = range(simulated_data$movement_time),
    maxit = 100
    )
```

```{r fitting-summary}
# fitting summary
summary(results)
```

We can then plot the underlying (latent) function(s). Note that this returns a `ggplot2` object that can be subsequently modified.

```{r latent}
plot(x = results, method = "latent", model_version = "TMM3") +
    labs(title = "Example of latent activation function")
```

We can also do "predictive checks" by comparing the data used to fit the model to data simulated from the model using the estimated parameter values.

```{r ppc}
plot(
    x = results, original_data = simulated_data,
    method = "ppc", model_version = "TMM3", action_mode = "imagined"
    )
```

We can also do another form of "predictive check" by comparing the quantile values of the original and simulated data.

```{r quantiles, out.width = "100%"}
plot(
    x = results, original_data = simulated_data,
    method = "quantiles", model_version = "TMM3", action_mode = "imagined"
    )
```

We can also visualise the trajectory in parameter space during optimisation interactively using `plotly` (not shown below, but you should try this).

```{r optimisation, eval = FALSE}
plot(x = results, method = "optimisation")
```

## References

Nalborczyk, L., Longcamp, M., Gajdos, T., Servant, M. & Alario, F.‐X. (in preparation). Modelling the onset and duration of imagined actions: Assessing a novel algorithmic model of motor imagery.

Nalborczyk, L., Longcamp, M., Gajdos, T., Servant, M. & Alario, F.‐X. (2024). Towards formal models of inhibitory mechanisms involved in motor imagery: A commentary on Bach et al. (2022). Psychological Research, 1‐4. <https://doi.org/10.1007/s00426-023-01915-8>. Preprint available at <https://psyarxiv.com/tz6x2/>.

## Getting help

If you encounter a bug or have a question please file an issue with a minimal reproducible example on [GitHub](https://github.com/lnalborczyk/momimi/issues).
