---
title: "Fitting the models"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{model-fitting}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
  )
```

```{r setup}
library(momimi)
```

# Modelling the inhibitory mechanisms involved in motor imagery

A large body of behavioural, electrophysiological, and neuroimaging empirical evidence suggests that the motor system is involved during motor imagery. This raises the "problem of inhibition of execution": Given the role of the motor system in providing the multisensory content of motor imagery, how is it possible for motor imagery not to lead to motor execution? It has been proposed that this may be achieved by modulating (e.g., upregulating) the execution threshold. Alternatively, this may be achieved by parallel inhibitory processes preventing execution during motor imagery. We propose a toy algorithmic model of the interplay between excitatory and inhibitory processes during motor imagery to disentangle the respective predictions of these propositions.

In this model, activation and inhibition curves are modelled as a rescaled lognormal function. The overall model structure is adapted from horse-race models of activation/inhibition patterns during response inhibition (e.g., [this paper](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0169320)). One important difference with these models, however, is that in the present model, the competition (the balance) between excitatory and inhibitory inputs is modelled throughout the entire trial to account for both reaction times (i.e., the time it takes to prepare and initiate execution/imagery) and movement times (i.e., the time it takes to execute/imagine an action).

# Simulating data from the model

...

# Fitting the model to empirical data

...
